---
title: "Baby Names Analysis"
output: html_notebook
---

Find populartiy of name
```{r}
myname <- babynames[which(babynames$name=="Tom"),]
myname <- myname[which(myname$gender=="M"),]
plot(myname$year, myname$count)
```

Find unique girl names every year

```{r}
girl_names <- babynames[which(babynames$gender=="F"),]
tb <- as.data.frame(table(girl_names$year))
plot(tb)
```

Function that finds most popular names in a year:
```{r}
toptennames <- function(gender, year) {
  ttn = babynames[which(babynames$gender == gender & babynames$year == year), ]
  topnames = ttn[order(ttn$count, decreasing = TRUE), ]
  return(topnames[(1:10), ])
}

print(toptennames("M", "2010"))
```

Generate a list of the ten names that, in 2014, were relatively popular for both baby boys and baby girls. To do this, use the following condition. For names for which there are at least 1000 people in the year with that name (could be boys or girls), compute the difference between boys and girls with the name. Then, we will call those names with the smallest magnitude difference between the two the most "gender neutral" names. To complete this objective:

```{r}
male = babynames[which(babynames$gender=="M" & babynames$year == 2014), ]
female = babynames[which(babynames$gender=="F" & babynames$year == 2014), ]
merged = merge(male, female, by.x = "name", by.y = "name")
mergeTop = merged[which(merged$count.x + merged$count.y > 1000), ]
mergeTop$diff = abs(mergeTop$count.x - mergeTop$count.y)
m = mergeTop[order(mergeTop$diff), ]
head(m,10)
```

